|

### 2022-10-04 paper_comparison/paper_comparison/paper_comparison.Rmd
section 2.1

Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values presented in the residual plot could be considered as an indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at the top-right of Figure [ref here]. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model.

Heterskedasticity refers to the presence of nonconst error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heterskedasticity on a residual plot is the inconsistent spread of the residuals at different x values. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure \ref{fig:commondepartures}, or the "left-triangle" and "right-triganle" shape where the smallest variance occurs at the edges of the x-axis.

Compared to non-linearity and heterskedasticity, non-normality is usually harder to be detected from a residual plot since scatter plot is not excel in revealing marginal distribution. A favourable graphical summarise for this task is the quantile-quantile plot. However, for a consistent comparison in the later part of this paper, residual plot will be the focus. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points that do not centralize around the horizontal zero line and unevenly distribute at both sides of the zero line. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the zero line as shown at the bottom-right of Figure \ref{fig:commondepartures}.

>>>>

Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values presented in the residual plot could be considered as an indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at the top-right of Figure  \ref{fig:commondepartures}. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model.

Heteroskedasticity refers to the presence of nonconstant error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heteroskedasticity on a residual plot is the inconsistent spread of the residuals across the horizontal axis. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure \ref{fig:commondepartures}, or the "left-triangle" and "right-triangle" shape where the smallest variance occurs at one side of the horizontal axis.

Compared to non-linearity and heteroskedasticity, non-normality is usually harder to detect from a residual plot since scatter plot do not readily reveal the marginal distribution. A favourable graphical summary for this task is the quantile-quantile plot. However, for a consistent comparison, residual plot will be the focus of this paper. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points do not center around the horizontal axis and there is an uneven distribution of the number points at both below and above the horizontal axis. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the horizontal axis as shown at the bottom-right of Figure \ref{fig:commondepartures}.
